Enrich the datasets with new columns.

### 2020-08-26 inst/analysis/analysis_stable.Rmd
Fixing tags

ast_sizes_prop <- ast_sizes %>% count(expr_resolved_ast_size, wt = nb_eval_calls) %>%
                      arrange(desc(expr_resolved_ast_size)) %>% 
                      mutate(proportion = n / nb_eval_calls) %>% 
                      mutate(cumulative = cumsum(proportion))

ast_size_one <- ast_sizes %>% filter(expr_resolved_ast_size == 1) 
nb_ast_size_one <- count(ast_size_one, wt = nb_ev_calls)$n
nb_ast_size_one_call_sites <- nb_eval_call_sites(ast_size_one)
r("nb ast one percent", ratio(nb_ast_size_one, nb_eval_calls))
r("nb ast one call site percent", ratio(nb_ast_size_one_call_sites, nb_call_sites))

@@

r("ast size 95", nb_nodes_many$expr_resolved_ast_size)
r("ast size 95 exact percent", percent(nb_nodes_many$proportion))

>>>>

ast_sizes_prop <- ast_sizes %>% count(expr_resolved_ast_size, wt = nb_eval_calls) %>%
                      mutate(proportion = n / sum(n)) %>% 
                      arrange(expr_resolved_ast_size) %>% 
                      mutate(cumulative = cumsum(proportion))

ast_size_one <- ast_sizes %>% filter(expr_resolved_ast_size == 1) 
nb_ast_size_one <- count(ast_size_one, wt = nb_ev_calls)$n
nb_ast_size_one_call_sites <- nb_eval_call_sites(ast_size_one)
r("nb ast one percent", ratio(nb_ast_size_one, sum(ast_sizes_prop$n)))
r("nb ast one call site percent", ratio(nb_ast_size_one_call_sites, nb_eval_call_sites(ast_sizes)))

@@

r("ast size nine five", nb_nodes_many$expr_resolved_ast_size)
r("ast size nine five exact percent", percent(nb_nodes_many$proportion))

### 2020-08-26 inst/analysis/enrich_dataset.Rmd
Fixing tags

```{r shrink_to_corpus}
corpus_files <- read_lines(CORPUS_FILE)
eval_calls <- eval_calls %>% keep_only_corpus(corpus_files)
```

@@

There are `r nrow(eval_calls)` unique rows.

```{r separate_datasets}
eval_calls_core <- eval_calls %>% filter(eval_source_type == "core")
eval_calls_packages <- eval_calls %>% filter(eval_source_type == "package" )
eval_calls_kaggle <- eval_calls %>% filter(eval_source_type == "kaggle")
```

@@

@@

r("undefined evals", nb_undefined$n)
r("percent undefined eval", ratio(nb_undefined$n, nb_eval_calls))
r("undefined eval expressions", nb_different_call_expr)
```

@@

write_fst(eval_calls_kaggle, EVALS_SUM_KAGGLE_FILE)
```

>>>>

@@

```{r shrink_to_corpus}
corpus_files <- read_lines(CORPUS_FILE)
eval_calls_corpus <- eval_calls %>% keep_only_corpus(corpus_files)

eval_calls_externals <- eval_calls %>% get_externals(corpus_files)
```

There are `r nrow(eval_calls)` unique rows. The file with dependent packages has `r nrow(eval_calls_externals)` rows and the one with only the packages in the corpus, `r nrow(eval_calls_corpus)`.

```{r separate_datasets}
eval_calls_core <- eval_calls_corpus %>% filter(eval_source_type == "core")
eval_calls_packages <- eval_calls_corpus %>% filter(eval_source_type == "package" )
eval_calls_kaggle <- eval_calls_corpus %>% filter(eval_source_type == "kaggle")
```

@@

nb_out_corpus <- undefined_evals %>% semi_join(eval_calls_externals) %>%
    count(wt = nb_ev_calls)

@@

r("undefined evals", nb_undefined$n)
r("percent undefined eval", ratio(nb_undefined$n, nb_eval_calls))
r("undefined eval expressions", nb_different_call_expr)
r("undefined out of corpus", nb_out_corpus)
r("undefined out of coprus percent", ratio(nb_out_corpus, nb_undefined))
```

@@

write_fst(eval_calls_kaggle, EVALS_SUM_KAGGLE_FILE)

write_fst(eval_calls_externals, EVALS_SUM_EXTERNALS_FILE)
```
